---
title: "Using data and tech for advocacy in times of a pandemic"
draft: no
date: '2020-04-24T00:00:00Z'
linktitle: Covid-19 Projects
summary: Communities using data and tech to voice their agendas during Covid-19
lastmod: '2020-04-24T00:00:00Z'
type: post
jquerydisable: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r source files}
source("../../assets/scripts/R/functions.R")
source("../../assets/scripts/R/packages.R")
```

```{r Read data from covid sheet}
covid_sheet_url <- "https://docs.google.com/spreadsheets/d/1vwWZzNsa2AxBcLeid88dU0RmmseyJiF2eMYJvberV4w/edit?usp=sharing"

all_form_responses <-
  read_other_sheets(sheet_url = covid_sheet_url)
names(all_form_responses)[] <- all_form_responses[6,]
all_form_responses <- all_form_responses[7:nrow(all_form_responses),]


all_form_responses$URL <-
    ifelse(
      !is.na(all_form_responses$URL),
      text_spec(
        all_form_responses$URL,
        link = all_form_responses$URL
      ),
      all_form_responses$URL
    )
```

_A list of data and tech projects around law, policy and advocacy in the times of Covid-19.  We wanted to curate this information at one place and share these initiatives with a wider audience, mainly for inspiration, collaboration and learning. A live version of this list can also be accessed [here](https://bit.ly/justicehub-covid)_

{{% alert note %}}
As Justice Hub, we would love to be a part of these initiatives and support them from a data and technology perspective. So, let us know if you're working on something similar, and we shall get back to you as soon as possible. 

_You can share the details [here](https://tinyurl.com/jh-covid-survey)_
{{% /alert %}}

```{r show table}
all_form_responses %>% DT::datatable(
  rownames = FALSE,
  class = 'cell-border stripe',
  escape = FALSE,
  filter = "top",
  options = list(pageLength = 10)
)
```